% Curriculum Vitae
% Inspiration and Structure from https://github.com/watsonbox/cv_template_2004
\documentclass[10pt]{article} % Default font size
\input{structure.tex} % Include the file specifying document layout

\settoggle{show}{false} % toggle to show gpa and other student-y stuff

\begin{document}

	% Title and Contact Info
	\huge{\color{slateblue}\textbf{Andrew Davis - CV}}\\ % Header section name and color
	\rule{\textwidth}{0.5mm}\\ % Rule under the header
	\small
	\begin{nstabbing}
		\hspace{1.5cm} \= \hspace{9cm} \= \hspace{1.5cm} \= \kill
		\textbf{Address}: \>17 Evergreen St., Boston, MA 02130 \> \textbf{Phone}: \> (443) 745-7990 \\
		\textbf{Website}: \> www.andrewdaviscomposer.com	\> \textbf{Email}: \> andrewdavis33@gmail.com
	\end{nstabbing}
	
	%	Education Section
	\section{Education}
	\tabbedblock{
	\bf{2018} \> M.S. in Computer Science | Stanford University
	\iftoggle{show}{\\  \> GPA: 4.0 | Advisor: Chris Gregg}{}
	}
	
	\tabbedblock{
		\bf{2017} \> Ph.D. in Music Composition | University of Pennsylvania
		\iftoggle{show}{\\
		\> GPA: 3.98 | Advisor: Anna Weesner \\
		\\
		\> \begin{minipage}{\smallertextwidth}
			Additional studies at Curtis Institute of Music in conducting under Paul Bryan and Jonathan Coopersmith 
		\end{minipage}
		}{}
	}
	
	\tabbedblock{
		\bf{2012} \> M.M. in Music Composition | University of Texas at Austin 
		\iftoggle{show}{\\\> GPA: 4.0 | Phi Kappa Pi }{}
	}
	
	\tabbedblock{
		\bf{2009}\> B.A. in Music | Yale University 
		\iftoggle{show}{\\\> GPA: 3.83 | Cum Laude | Distinction in the Major}{}
	}
	
	\section{Academic Positions}
	
	\jobMultiLine
	{July 2018 -}{Present}
	{Wellesley College}
	{Lecturer in Computer Science and Media Arts and Sciences}
	
	\section{Major Academic Projects}
	
	\project{Sept. 2020 - }{Present}{\textit{sckernel}: a kernel for Jupyter Notebooks}{\url{https://github.com/andrewdavis33/sckernel}}{
	\textit{sckernel} is a kernel for Jupyter Notebooks, an online platform for interactive code.  Jupyter Notebooks
	provide a clean, easy-to-read interface for interactive Python code.  The framework for Jupyter Notebooks
	allows for user-written kernels to support programming languages besides Python.  \textit{sckernel} integrates
	with Jupyter Notebooks to provide web-based interaction with SuperCollider.
	}
	
	\project{June 2020 - }{Present}{Introductory Resources for DFT Analysis and Synthesis}{\url{https://github.com/andrewdavis33/DFT-Guide}}
	{
		A comprehensive, introductory guide to Discrete Fourier Transform in the context of audio for musicians and programmers.  Much material
		for signal processing and Fourier analysis is too arcane for introductory students.  
		This guide serves to lead newcomers through an intuitive derivation of the DFT and uses musical examples to articulate important theoretical and practical concepts.  Future work for the project
		involves creating visual demonstrations and short YouTube videos to better illustrate principles of the DFT.
	}
	
	\project{July 2018 - }{Present}{Instrument and Effect Software for the SuperCollider Platform}{\url{https://github.com/andrewdavis33/sc_library}}{
		A repository of musical instruments, synthesizers, and effects written in sclang for the SuperCollider platform.
		Examples of files range from experimental reverberators to traditional 80's synth effects.  Future work includes
		development of Fourier techniques as well as UGens for server-side processing.
	}
	
	\newpage
	\section{Teaching Experience}
	
	\smallHeader{Wellesley College}
	
	\positionBlock{Fall 2018 -}{Present}{Primary Lecturer:
		I have taught all classes below multiple times as the primary lecturer.  \textit{Introduction to Computer
		Music} was designed from scratch by myself, including all slides, assignments, and website.  I have
		taught \textit{Computer Programming and Problem Solving Methodologies} in a team format where
		multiple instructors teach separate sections of the same course but work together to devise course
		content and structure as well as manage student needs for an introductory course of over 100 students
		per semester.\\
		\\
		\textit{Introduction to Computer Music}: \url{https://cs.wellesley.edu/~cs203/}\\
		Self-designed, interdisciplinary course spanning topics on music, computers and mathematics\\
		\\
		\textit{Computer Programming \& Problem Solving}: \url{https://cs.wellesley.edu/~cs111}\\
		First course in programming for CS majors on programming paradigms, recursion, and data structures \\
		\\
		\textit{Foundations of Computer Systems}: \url{https://cs.wellesley.edu/~cs240}\\
		An introduction to software systems, machine organization, and architecture, and digital logic 
	}
	
	\smallHeader{Stanford University}
	
	\positionBlock{Winter 2018 -}{Summer 2018}{Graduate Assistant:
		I served as a graduate assistant for the courses listed below.  My main duties included holding office
		hours on campus and answering questions about course content through Piazza.\\
		\\
		\textit{Probability for Computer Scientists}: \url{http://web.stanford.edu/class/cs109/}\\
		A mathematical overview of topics from basic counting to logistic regression\\
		\\
		\textit{Programming Methodology}: \url{http://web.stanford.edu/class/cs106a/}\\
		First course in programming for CS majors on object-oriented design, decomposition, encapsulation, and abstraction
	}
	
	\smallHeader{University of Pennsylvania}
	
	\positionBlock{Fall 2014 -}{Spring 2016}{Graduate Assistant:
		I taught a range of introductory music courses.  Though I was a graduate student, I was the
		primary instructor for all courses listed below.  I was responsible for curriculum development
		for both musicianship courses.\\
		\\
		\textit{Introductory Theory and Musicianship}\\
		An introduction to the basics of music notation, theory, and ear-training for non-music majors\\
		\\
		\textit{Music Theory and Labratory II} \\
		Second course in musicianship designed for first-year and sophomore music majors\\
		\\
		\textit{Music Theory and Labratory I}\\
		First course in musicianship designed for first-year and sophomore music majors
	}
	
	\section{Service Experience}
	\smallHeader{Wellesley College}
	
	\positionBlock{Fall 2019 -}{Present}{
		\textit{Tutoring Coordinator}:
		The tutor coordinator manages tutors across the department and serves as liaison between the 
		department and the learning center on campus that governs tutoring across the College.  The 
		tutor coordinator organizes tutor training and coordinates with faculty to hire tutors.
	}
	
	\positionBlock{Fall 2019 - }{Spring 2020}{
		\textit{Curriculum Committee Member}:
		The Curriculum Committee is responsible for evaluating and amending the department's offering
		of courses.  The Curriculum Committee works with the department's Diversity and Inclusion
		Committee to assess the impact of the department's offerings on inclusion.  During my time on
		the committee, we submitted a formal proposal to change the  introductory sequence from a 
		two-course model to a three-course model to alleviate the quick pace of the sequence and to 
		better match students' previous exposure with CS to the appropriate course.  We expect the
		proposal to be approved and implented by the College shortly.  
	}
	
	\positionBlock{Fall 2019 -}{Present}{
		\textit{CS Advisor}: CS Advisors advise CS majors and minors by planning out course schedules,
		advising on internships, and offering advice on career paths.   I have advised 11 CS majors and minors
		during my time as a CS Advisor.
	}
	
	\positionBlock{Fall 2019 -}{Present}{
		\textit{First-Year Advisor}: First-Year Advisors serve a term of three years and mentor six first-year
		students each year.  First-Year Advisors' are responsible for helping students choose 
		courses that match their interests and ensuring that students understand distributional
		requirements and create a balanced schedule.
	}
	
	\positionBlock{Fall 2019 -}{Present}{
		\textit{CS Poster Advisor}: CS Poster Advisors work with two seniors each year and guide them
		through a year-long project that culminates in department-wide poster session.  Topics 
		on which I have advised have ranged from algorithmic design in neuroscience to AI studies on
		music recognition.
	}
	
	\section{Composition Awards}
	
	\achievement{2021}{NYC Contemporary Music Symposium: Finalist - \textit{Night Visions}}
	\achievement{2020}{C4's IGNITE Commissioning Competition: Semifinalist}
	\achievement{2020}{MACRO Composition Contest: Winner - \textit{Speechless}}
	\achievement{2019}{Boston New Music Initiative 7th Annual Commissioning Competition: Winner}
	\achievement{2018}{Sioux City Symphony Orchestra Composer of the Year: Honorable Mention - \textit{Seek}}
	\achievement{2017}{Chaosfl{\"o}te Commissioning Competition: Honorable Mention - \textit{I Walk The Path Before Me}}
	\achievement{2017}{American Composers Orchestra Underwood Readings: Honorable Mention: \textit{Seek}}
	\achievement{2016}{Luna Nova Composition Contest: 2nd Prize - \textit{Hummingbirds}}
	\achievement{2015}{Flute New Music Consortium: Semifinalist - \textit{What's Next?}}
	\achievement{2015}{Col Legno duo Composition Contest: Honorable Mention}
	\achievement{2015}{ASCAP Morton Gould Awards: Finalist - \textit{The Deep End}}
	\achievement{2015}{Lyra Society Costello Composition Competition: 2nd Prize}
	\achievement{2015}{Halstead Prize from the University of Pennsylvania - \textit{Nocturne}}
	\achievement{2014}{ASCAP Morton gould Awards: Finalist - \textit{Black Mamba}}
	\achievement{2013}{MACRO Competition: Honorable Mention - \textit{Open Airs}}
	\achievement{2013}{BMI Student Composer Award: Finalist - \textit{Midnight Drearies}}
	\achievement{2013}{ASCAP Plus Award}
	\achievement{2012}{ASCAP Plus Award}
	\achievement{2012}{Boston New Music Initiative Commissioning Competition: Finalist - \textit{Black Mamba}}
	\achievement{2012}{Choral New Music Initiative: Winner - \textit{Holidays}}
	
	\section{Commissions}
	
	\achievement{2019}{Boston New Music Initiative and Cambridge Chamber Singers: \textit{On The Nature of Things}}
	\achievement{2019}{Andrew Harrison, Saxophonist and Mt. San Antonio String Orchestra: \textit{Serenade}}
	\achievement{2017}{loadbang and the RED NOTE New Music Festival: \textit{Spitballing}}
	\achievement{2016}{Atlantic Music Festival: \textit{Hummingbirds}}
	\achievement{2015}{Lyra Society of Philadelphia: \textit{Sing Sweetly, Run Swiftly}}
	\achievement{2014}{Michael Harley, Bassoonist of Alarm Will Sound: \textit{What's Next?}}
	\achievement{2014}{Alexandra Porter, Soprano: \textit{Bamboo Grove?}}
	\achievement{2013}{Alarm Will Sound and the Mizzou International Composer Festival: \textit{The Deep End}}
	\achievement{2012}{Charlie Magnone, Pianist: \textit{Night Visions}}
	
	\section{Juried Compositional Festivals And Conferences}
	
	\achievement{2021}{SEAMUS National Conference: \textit{Pastoral}}
	\achievement{2021}{Earth Day Art Model: \textit{Poetry of the Earth}}
	\achievement{2020}{New York City Electronic Music Festival: \textit{Poetry of the Earth}}
	\achievement{2019}{TUTTI Festival at Denison University: \textit{Nocturne}}
	\achievement{2017}{TUTTI Festival at Denison University: \textit{I Walk The Path Before Me}}
	\achievement{2017}{RED NOTE New Music Festival}
	\achievement{2016}{Belvedere Chamber Music Festival: \textit{Hummingbirds}}
	\achievement{2016}{Atlantic Music Festival}
	\achievement{2015}{World Association of Symphonic Bands and Ensembles: \textit{The River Jumped Over The Mountain}}
	\achievement{2014}{Bowling Green State University Graduate Conference: \textit{Open Airs}}
	\achievement{2013}{Mizzou International Composers Festival}
	\achievement{2013}{Manchester New Music Mini-Festival: \textit{Funk Off}}
	\achievement{2013}{16th Festival of New Music at FSU: \textit{The River Jumped Over The Mountain}}
	\achievement{2012}{New Music on the Point Festival}
	\achievement{2011}{SEAMUS/ASCAP Festival: \textit{Spratonic}}
	
	\section{Conference Presentations}
	
	Davis, Andrew (2021).  \textit{Integrating SuperCollider with Jupyter Notebooks}.  Presented at the
	    2021 SEAMUS Virtual National Conference, USA.
	
	\section{Compositional Discography}
	
	\achievement{2020}{``Night Visions". Petrichor Records; \emph{New Music by Living Composers}. Category A - Solo Piano}
	\achievement{2017}{``Five Poisons". Andrew Harrison and Clare Longendyke; \emph{In the City: New Works for Saxophone and Piano}}
	\achievement{2016}{``Funk Off". The TC4; \emph{TC4}}
	\achievement{2014}{``Black Mamba." Contemporary Art Music in Texas; Limited Distribution for the 2012 ISCM World Music Days}
	
	\section{Score Publications}
	
	\achievement{2016}{``Sing Sweetly, Run Swiftly".  Fatrock, Inc.}
	
	\section{Guitar Discography}
	
	\achievement{2019}{Hawk Tubley and the Ozymandians: \emph{Chocolate Maple Squeeze Play}}
	\achievement{2016}{Hawk Tubley and the Ozymandians: \emph{Pond Kings in April}}
	
	\section{Notable Performing Groups}
	
	\bulletPoint{Alarm Will Sound}
	\bulletPoint{PRISM Saxophone Quartet}
	\bulletPoint{Daedalus Quartet}
	\bulletPoint{ETHEL Quartet}
	\bulletPoint{JACK Quartet}
	\bulletPoint{Aizuri Quartet}
	\bulletPoint{loadbang}
	\bulletPoint{Argento Ensemble}
	\bulletPoint{Curtis Symphony Orchestra}
	\bulletPoint{Skyros Quartet}
	\bulletPoint{Florida State Wind Ensemble}
	\bulletPoint{Yale Concert Band}
	
	\section{Grants}
	
	\achievement{2014}{American Composers Forum Philadelphia Subito Grant}
	\achievement{2013 - 2017}{Benjamin Franklin Scholarship at the University of Pennsylvania}
	\achievement{2010 - 2012}{Kent Kennan Endowed Graduate Fellowship}
	
	\section{Artistic Residencies}
	
	\achievement{2017}{Atlantic Center for the Arts}
	\achievement{2016}{ACRE}
	\achievement{2015}{Atlantic Center for the Arts}
	
	\section{Miscellaneous}
	\achievement{2009}{Assistant Producer for NFL Films | Emmy Nomination for NFL Weekly Countdown }
	\achievement{2009}{Intern at Strathmore Center for the Arts}
	\achievement{2008}{Intern at Wolf Trap National Park for the Performing Arts}
	
	\section{Software Engineering Skills}
	
	\skillgroup{Music Programming Languages}{
		\textit{SuperCollider}, \textit{Max/MSP}, \textit{ChucK}
	}
	
	\skillgroup{Programming Languages}{
		\textit{C}, \textit{C++}, \textit{Python}, \textit{Java}, \textit{MATLAB}
	}
	
	\skillgroup{Web Development}{
		\textit{HTML5}, \textit{CSS3/SASS}, \textit{JavaScript}, \textit{Jekyll}\\
	}

	%\section{Diversity Training}
	%\achievement{2020}{21 Days Against Racism}
	%\achievement{2021}{Change Agent Training}
	
	\section{Professional Societies and Affiliations}
	
	\bulletPoint{ASCAP}
	\bulletPoint{ACM}
	\bulletPoint{American Composers Forum}
	\bulletPoint{SEAMUS (Society for Electroacoustic Music United States)}
	
	\section{References}
	
	\reference{Anna Weesner}{Univ. of Pennsylvania}{Professor of Music}{weesner@sas.upenn.edu}{(215) 898-7544}
	\tabto{3.5in}
	\reference{James Primosch}{Univ. of Pennsylvania}{Professor of Music}{primosch@sas.upenn.edu}{(215) 898-7544}\\
	\reference{Chris Gregg}{Stanford University}{Lecturer of Computer Science}{cgregg@stanford.edu}{(857) 234-0211}
	\tabto{3.5in}
	\reference{Jay Reise}{Univ. of Pennsylvania}{Professor of Music}{jreise@sas.upenn.edu}{(215) 898-7544}

\end{document}